Response to reviewers and editorial comments for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2023-01-19 src/docs_review/review.Rmd
Update COI statement

Response here.
Requested that coauthors send their COIs.

>>>>

The competing interests' statement has been updated to the following:

> I have read the journal's policy and the authors of this manuscript have the following competing interests: KAR was supported through a consultancy via UNAIDS to conduct an early version of this work;  LZ, IW, MM, and CB are employees of UNAIDS; JWE is a member of the editorial board for PLOS GPH; other authors have declared that no competing interests exist.
